R for Clinical Study Reports and Submission

### 2021-11-17 tlf-efficacy-km.Rmd
update renv.lock

First, to prepare the analysis ready data, filter all records for the efficacy endpoint of TTDE using `PARAMCD` (or `PARAM`, `PRAMN`), then select the survival analysis related variables:

@@

The `survival` package is used to create the curve data points, then `survminer` package can be used to plot the K-M curve with an elegant ggplot2 style. There are tons of customized options for users to create a K-M plot with risk table and testing result (nominal p-value). More details can be found in `?survminer::ggsurvplot`.

Users can use `Surv()` with formula directly, or use a fitted Cox model with the `coxph()` function if also want to obtain other information, i.e. hazard ratio, survival rates, etc. <!-- TODO: "Analysis of Survival Endpoint Table" Chapter -->

```{r}
fit <- survfit(Surv(AVAL, 1 - CNSR) ~ TRTP, data = adtte_ttde)
# sum_fit <- summary(coxph(Surv(AVAL, 1-CNSR) ~ ARM  + strata(STRATAP), data = adtte_efs))
fig_km <- ggsurvplot(
  fit,
  xlab = "Time in Months",
  ylab = "Survival Probability",
  break.time.by = 30.4367,
  xscale = "d_m",
  xlim = c(0, 200),
  linetype = c(1, 2, 3),
  risk.table = TRUE,
  risk.table.height = 0.3, # Useful when you have multiple groups
  legend = c(0.8, 0.9), legend.title = "",
  legend.labs = sort(unique(adtte_ttde$TRTP)),
  censor.size = 4,
  size = 0.8,
  title = "",
  censor.shape = "|",
  pval = TRUE,
  pval.method = TRUE,
  pval.coord = c(0, 0.1),
  pval.method.coord = c(0, 0.2),
  pval.size = 5,
  ggtheme = theme_classic2(base_family = "Times New Roman", base_size = 18)
)
```

>>>>

First, to prepare the analysis ready data, 
filter all records for the efficacy endpoint of time to event of interest (`TTDE`) 
using `PARAMCD` (or `PARAM`, `PRAMN`), then select the survival analysis related variables:

@@

The `survival` package is used to create the curve data points, 
then `survminer` package can be used to plot the K-M curve with an elegant `ggplot2` style. 
There are tons of customized options for users to create a K-M plot
with risk table and testing result (nominal p-value). 
More details can be found in `?survminer::ggsurvplot`.

Users can use `Surv()` with formula directly, 
or use a fitted Cox model with the `coxph()` function 
if we also want to obtain other information, i.e. hazard ratio, survival rates, etc. 
<!-- TODO: "Analysis of Survival Endpoint Table" Chapter -->

```{r}
fit <- survfit(Surv(AVAL, 1 - CNSR) ~ TRTP, data = adtte_ttde)
```

```{r}
sum_fit <- summary(coxph(Surv(AVAL, 1-CNSR) ~ ARM  + strata(STRATAP), data = adtte_efs))
```

```{r}
fig_km <- ggsurvplot(
  fit,
  xlab = "Time in Months",
  ylab = "Survival Probability",
  break.time.by = 30.4367,
  xscale = "d_m",
  xlim = c(0, 200),
  linetype = c(1, 2, 3),
  risk.table = TRUE,
  risk.table.height = 0.3, # Useful when you have multiple groups
  legend = c(0.8, 0.9), legend.title = "",
  legend.labs = sort(unique(adtte_ttde$TRTP)),
  censor.size = 4,
  size = 0.8,
  title = "",
  censor.shape = "|",
  pval = TRUE,
  pval.method = TRUE,
  pval.coord = c(0, 0.1),
  pval.method.coord = c(0, 0.2),
  pval.size = 5,
  ggtheme = theme_classic2(base_family = "Times New Roman", base_size = 18)
)
```
